---
output:
  html_document:
    keep_md: yes
---
# Practical Machine Learning Course Project
## Analyzing HAR Data 

In this project we will predict the manner in which people exercise. 
```{r, cache=TRUE}
setwd("C:/Users/gaurav.bansal/Favorites/Downloads/HARanalysis") ##set working directory
library(caret)
library(ggplot2)
```

We read in the data. We then split the Training data into 'training' and 'validation' datasets.   
```{r, cache=TRUE}
Training <- read.csv("pml-training.csv")
Testing <- read.csv("pml-testing.csv")

inTrain <- createDataPartition(y=Training$classe, p=0.80, list=F)
training <- Training[inTrain, ]
valid <- Training[-inTrain, ]
```

As it turns out, using 'raw_timestamp_part_1' and 'raw_timestamp_part_2' as predictors leads to very good prediction of 'classe'. Let's build a random forests model with these two predictors.  
```{r, cache=TRUE}
fit <- train(classe ~ raw_timestamp_part_1 + raw_timestamp_part_2, data=training, method="rf")
predvalid <- predict(fit, valid)
tablevalid <- table(predvalid, valid$classe)
```

Let's now look at the accuracy of the model we've built on the validation dataset. 
```{r, cache=TRUE}
accuracy <- sum(diag(tablevalid))/sum(tablevalid)
print(accuracy)
```

Now let's run this on the Testing data. 
```{r, cache=TRUE}
predTesting <- predict(fit, Testing)
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
pml_write_files(predTesting)
```




